### 2013-07-31 doc/taxize_withcode_plos.Rnw
a few spelling changes to ms, added cover letter

I may happen that a data source does not provide information on the querried species, than one could take the result from another source and union the results from the different sources.

@@

<<phylomaticphylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE, include=FALSE>>=
# Input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

@@

\subsection*{Matching species tables with different taxonomic resolution}
Biologist often need to match different sets of data tied to species. For example, trait-based approaches are a promising tool in ecology \cite{statzner_can_2010}. One problem is that abundance data must be matched with trait databases like \cite{usseglio-polatera_biological_2000}. These two data tables may contain species information on different taxonomic levels and possibly data must be aggregated to a joint taxomic level, so that the data can be merged. taxize can help in this data-cleaning step, providing a reproducible workflow:

@@

We see that the two Juncus species are aggregated to Juncaceae and their abundances are summed up. If a taxon is one lower taxonomic resolution then the querried or the taxon is not found in the database then these are not aggregated and returned as is.

@@

\section*{Figure Legends}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4in]{figure/phylomaticphylogeny.pdf}
\end{center}
\caption{
{\bf A Phylogeny for the three species.}
}
\label{fig:phylomatic}
\end{figure}

@@

\begin{table}[!ht]
\caption{
\bf{Some key functions in taxize, what they do, and their data sources}}
\begin{tabular}{|l|L|L|}
\hline
Function name & What it does & Source \\
\hline
apg\_lookup & Changes names to match the APGIII list & Angiosperm Phylogeny Group \cite{apgiii}  \\
classification & Upstream classification & Various  \\
col\_children & Direct children & Catalogue of Life \cite{col}  \\
col\_downstream & Downstream taxa to specified rank & Catalogue of Life \cite{col}  \\
eol\_hierarchy & Upstream classification & Encyclopedia of Life \cite{eol}  \\
eol\_search & Search EOL taxon information & Encyclopedia of Life \cite{eol}  \\
get\_seqs & Get NCBI sequences & National Center for Biotechnology Information \cite{federhen}  \\
get\_tsn & Get ITIS TSN & Integrated Taxonomic Information System \cite{itis}  \\
get\_uid & Get NCBI UID & National Center for Biotechnology Information \cite{federhen}  \\
searchbycommonname & Search ITIS by common name & Integrated Taxonomic Information System \cite{itis}  \\
searchbyscientificname & Search ITIS by scientific name & Integrated Taxonomic Information System \cite{itis}  \\
gisd\_isinvasive & Inasiveness status & Global Invasive Species Database \cite{gisd}  \\
gni\_parse & Parse scientific names into components & Global Names Index \cite{eol,eolgni}   \\
gni\_search & Search EOL's global names index & Global Names Index \cite{eol,eolgni}   \\
gnr\_resolve & Resolve names using EOL's global names index & Global Names Resolver \cite{eol,eolgnr}  \\
itis\_downstream & Downstream taxa to specified rank & Integrated Taxonomic Information System \cite{itis}  \\
iucn\_status & IUCN status & IUCN Red List \cite{iucn}  \\
phylomatic\_tree & Get a plant Phylogeny & Phylomatic \cite{webb2005}  \\
plantminer & Search Plantminer & Plantminer \cite{carvalho2010plantminer}   \\
tax\_name & Get taxonomic name for specific rank & Various  \\
tax\_rank & Get rank of a taxonomic name & Various  \\
tnrs & Resolve names using iPlant & iPlant Taxonomic Name Resolution Service \cite{tnrs}  \\
tp\_acceptednames & Check for accepted names using Tropicos & Tropicos \cite{tropicos}  \\
tpl\_search & Search the Plant List & The Plant List \cite{theplantlist}  \\
ubio\_namebank & Search uBio & uBio \cite{ubio}  \\
\hline
\end{tabular}
\label{tab:a}
\end{table}

>>>>

I may happen that a data source does not provide information on the queried species, than one could take the result from another source and union the results from the different sources.

@@

<<phylomaticphylogeny, eval=TRUE, dev=c ('pdf','tiff'), dpi=300, out.width='4in', out.height='4in', cache=TRUE, include=FALSE>>=
# Input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

@@

\subsection*{Matching species tables with different taxonomic resolution}
Biologist often need to match different sets of data tied to species. For example, trait-based approaches are a promising tool in ecology \cite{statzner_can_2010}. One problem is that abundance data must be matched with trait databases like \cite{usseglio-polatera_biological_2000}. These two data tables may contain species information on different taxonomic levels and possibly data must be aggregated to a joint taxonomic level, so that the data can be merged. taxize can help in this data-cleaning step, providing a reproducible workflow:

@@

We see that the two \emph{Juncus} species are aggregated to Juncaceae and their abundances are summed up. If a taxon is one lower taxonomic resolution then the queried or the taxon is not found in the database then these are not aggregated and returned as is.

@@

\section*{Figure Legends}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4in]{figure/phylomaticphylogeny.pdf}
\end{center}
\caption{
{\bf A phylogeny for three species. This phylogeny was produced using the \emph{phylomatic\_tree} function, which queries the Phylomatic database, and prunes a previously created phylogeny of plants.}
}
\label{fig:phylomatic}
\end{figure}

@@

\begin{table}[!ht]
\caption{
\bf{Some key functions in taxize, what they do, and their data sources}}
\begin{tabular}{|l|L|L|}
\hline
Function name & What it does & Source \\
\hline
apg\_lookup & Changes names to match the APGIII list & Angiosperm Phylogeny Group \cite{apgiii}  \\
classification & Upstream classification & Various  \\
col\_children & Direct children & Catalogue of Life \cite{col}  \\
col\_downstream & Downstream taxa to specified rank & Catalogue of Life \cite{col}  \\
eol\_hierarchy & Upstream classification & Encyclopedia of Life \cite{eol}  \\
eol\_search & Search EOL taxon information & Encyclopedia of Life \cite{eol}  \\
get\_seqs & Get NCBI sequences & National Center for Biotechnology Information \cite{federhen}  \\
get\_tsn & Get ITIS TSN & Integrated Taxonomic Information System \cite{itis}  \\
get\_uid & Get NCBI UID & National Center for Biotechnology Information \cite{federhen}  \\
searchbycommonname & Search ITIS by common name & Integrated Taxonomic Information System \cite{itis}  \\
searchbyscientificname & Search ITIS by scientific name & Integrated Taxonomic Information System \cite{itis}  \\
gisd\_isinvasive & Invasiveness status & Global Invasive Species Database \cite{gisd}  \\
gni\_parse & Parse scientific names into components & Global Names Index \cite{eol,eolgni}   \\
gni\_search & Search EOL's global names index & Global Names Index \cite{eol,eolgni}   \\
gnr\_resolve & Resolve names using EOL's global names index & Global Names Resolver \cite{eol,eolgnr}  \\
itis\_downstream & Downstream taxa to specified rank & Integrated Taxonomic Information System \cite{itis}  \\
iucn\_status & IUCN status & IUCN Red List \cite{iucn}  \\
phylomatic\_tree & Get a plant Phylogeny & Phylomatic \cite{webb2005}  \\
plantminer & Search Plantminer & Plantminer \cite{carvalho2010plantminer}   \\
tax\_name & Get taxonomic name for specific rank & Various  \\
tax\_rank & Get rank of a taxonomic name & Various  \\
tnrs & Resolve names using iPlant & iPlant Taxonomic Name Resolution Service \cite{tnrs}  \\
tp\_acceptednames & Check for accepted names using Tropicos & Tropicos \cite{tropicos}  \\
tpl\_search & Search the Plant List & The Plant List \cite{theplantlist}  \\
ubio\_namebank & Search uBio & uBio \cite{ubio}  \\
\hline
\end{tabular}
\label{tab:a}
\end{table}
